---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dod

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/dod)](https://CRAN.R-project.org/package=dod)
<!-- badges: end -->

The goal of dod is to make it easier to download various types of oceanographic data from common sources such as BATS, NAOO, MEDS, BBMP. 

## Installation

You can install the development version of dod from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AnnieHow/dod")
```

## Example

The following example shows how to download ctd index from the BBMP program in the year 2022 and download, read and plot the first item in the index using the `oce` package.

```{r example}
library(dod)
library(oce)
index <- dod.ctd("BBMP", 2022, index=TRUE) 
item <- index[1,"file"]
file <- dod.ctd("BBMP", 2022, item)
plot(read.ctd(file))
```


