---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dod

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/dod)](https://CRAN.R-project.org/package=dod)
[![R-CMD-check](https://github.com/dankelley/dod/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/dankelley/dod/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of dod is to make it easier to download various types of oceanographic data from common sources such as BATS, NAOO, MEDS, BBMP. Some similar functions exist in the oce package, but the intention is to retire them as dod matures, because building oce is difficult for some users, and CRAN policies dictate against frequent updates.

## Installation

You can install the development version of dod from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AnnieHow/dod")
```

## Example

The following example shows how to (1) download an index of ctd data files resulting from observations made as part of the BBMP program in the year 2022 and then (2) use functions in the oce package to read and plot the first file in that index.

```{r example}
# 1. Get index
library(dod)
index <- dod.ctd("BBMP", 2022, index=TRUE)
item <- index[1, "file"]
# 2. Get the first file, and plot it
file <- dod.ctd("BBMP", 2022, item)
library(oce)
plot(read.ctd(file))
```


