---
title: "Downloading Buoy Data"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
    number_sections: true
    fig_caption: yes
    fig_width: 3.5
    fig_height: 3.5
    dpi: 72
    dev.args: list(pointsize=11)
vignette: >
  %\VignetteIndexEntry{Downloading Buoy Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The basics of downloading buoy data are outlined in this
vignette, as a supplement to a shorter entry in the [main vignette](dod_package.html).

# Basics
The function `dod.buoy` can download buoy data from the Marine Environmental Data Section (MEDS).

# Finding Desired ID

In `dod.buoy` **ID** is the MEDS code for the region of interest or for the list below, the name of the region can be given: 

|       **Region Name**         | **Region ID** |
|                         :---- |         :---- |
|East Scotian Slope             | 44137         |
|Banquereau Bank                | 44139         |
|Halifax Harbour                | 44258         |
|Halifax                        | 44172         |
|Halifax DISCUS TriAx           | 44299         |
|Tail of the Bank               | 44140         |
|Laurentian Fan                 | 44141         |
|Port Hope                      | 45135         |
|Prince Edward Point            | 45135         |
|Minas Basin                    | MEDS027       |

# Example: Downloading MEDS Data

This is a basic example which shows you how to download buoy data from the MEDS server.

```{r example}
library(dod)
file <- dod.buoy("MEDS", ID="East Scotian Slope") 
```

