---
title: "Downloading ctd Data"
author: "Annie Howard"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
    number_sections: true
    fig_caption: yes
    fig_width: 3.5
    fig_height: 3.5
    dpi: 72
    dev.args: list(pointsize=11)
vignette: >
  %\VignetteIndexEntry{Downloading ctd Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<!-- HOW TO BUILD THE VIGNETTE. -->
<!-- 1. edit this file in vignettes/ctd.Rmd -->
<!-- 2. in an R console, use setwd() or otherwise move to the oce -->
<!--    directory, and then execute -->
<!--      devtools::build_vignettes() -->
<!-- 3. build oce. In the shell, you might use -->
<!--      cd oce ; echo "devtools::document(roclets=c('rd','collate','vignette'))" | R --no-save -->
<!--      CMD build --compact-vignettes="qpdf" oce -->
<!--      R CMD check oce_1.1-0.tar.gz -->
<!--      R CMD INSTALL oce_1.1-0.tar.gz -->
<!--    where the version number might need updating, or in an R console you might use -->
<!--      devtools::install(build_vignettes=TRUE) -->


```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

The basics of downloading CTD data are outlined in this
vignette, as a supplement to a shorter entry in the [main vignette](dod_package.html).

# Basics
The function `dod.ctd` can download ctd data from the Bedford Basin Mooring Program (BBMP), Bermuda Atlantic Time Series (BATS), Global Temperature and Salinity Program (GTSPP) etc by calling their respective functions `dod.ctd.bbmp`, `dod.ctd.bats` or `dod.ctd.gtspp`.

# Finding Desired ID
## BBMP 

In the `dod.ctd.bbmp` function, `ID` is the desired file from the index. Once the index is downloaded using the `dod.ctd` function, provide the file name from the index you want to download for the argument `ID`. **eg** ID= "D22667034.ODF"

## BATS

For BATS, `ID` is the 5 digit cruise ID. From BATS documentation, cruise ID format is as follows:

  8 digit cast_ID 	
        $XXXX###  where,

	$= cruise type
	1=bats core
	2=bats bloom a
	3=bats bloom b
 	5=bats validation
    6=Hydrostation
	9=Ancillary cruise
	XXXX= cruise number
	### = cast number

**eg.**	10155005  = bats core cruise, cruise 155, cast 5

**eg.**	50050005  = bats validation , cruise 50 , cast 5

## GTSPP

For GTSPP, `ID` is 8 digits in the following format:

XX####//  where,
	X=ocean basin initial (at, pa, in)
	#=year of interest
	/=month of interest
	
**eg** To attain data from the Atlantic in January 1985 input: ID="at198501". 

# Example: Downloading BBMP Data

This is a basic example which shows you how to download ctd index from the BBMP program in the year 2022 and download, read and plot the first item in the index using the `oce` package.

```{r example}
library(dod)
library(oce)
index <- dod.ctd("BBMP", 2022, index=TRUE, file="bbmp.txt") 
item <- index[1,"file"]
file <- dod.ctd("BBMP", 2022, item, file="bbmp.txt")
plot(read.ctd(file))
```



